SDR enhancement by clouds

### 2024-03-15 GHI_enh_04_investigate.tex
Commit 2024-03-15 19:11

@@

Arima: 354.314467 +/- 35.576408

@@

Arima: 127.193673 +/- 11.405953

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-2} \end{center}

@@

@@

\begin{verbatim}
2024-03-15 10:49:24.4 athan@tyler GHI_enh_04_investigate.R 1.189463 mins
\end{verbatim}

>>>>

\begin{verbatim}
Registered S3 methods overwritten by 'ggpp':
  method                  from   
  heightDetails.titleGrob ggplot2
  widthDetails.titleGrob  ggplot2
\end{verbatim}

\begin{verbatim}

Attaching package: 'ggpp'
\end{verbatim}

\begin{verbatim}
The following object is masked from 'package:ggh4x':

    stat_centroid
\end{verbatim}

\begin{verbatim}
The following object is masked from 'package:ggplot2':

    annotate
\end{verbatim}

\begin{verbatim}
Registered S3 method overwritten by 'ggpmisc':
  method                  from   
  as.character.polynomial polynom
\end{verbatim}

@@

lmY: 8.781482 +/- 0.831715

{[}1{]} -17410.99
{[}1{]} 8.781482
(Intercept) dataset\$year
-17410.988738 8.781482

\begin{verbatim}
`geom_smooth()` using formula = 'y ~ x'
\end{verbatim}

@@

@@

\hypertarget{monthly-energy-contribution-of-enhancements}{%
\subsubsection{Monthly Energy contribution of enhancements}\label{monthly-energy-contribution-of-enhancements}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-7} \end{center}

@@

\begin{verbatim}
2024-03-15 17:07:40.1 athan@tyler GHI_enh_04_investigate.R 1.283610 mins
\end{verbatim}

### 2024-03-15 article/article.Rmd
Commit 2024-03-15 19:11

output: 
 #  rticles::mdpi_article:
 #    extra_dependencies:  longtable
 #    keep_tex:            yes
  bookdown::pdf_document2:
    number_sections:  yes
    fig_caption:      yes
    keep_tex:         no
    latex_engine:     xelatex
    toc:              yes
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:    article
    classoption:      a4paper,oneside
    fontsize:         12pt
    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations:   yes
    colorlinks:       yes
    urlcolor:         blue
    biblio-style:     apalike
    bookdown::word_document2: default
---

>>>>

output: 
 #  rticles::mdpi_article:
 #    extra_dependencies:  longtable
 #    keep_tex:            yes
  bookdown::pdf_document2:
    number_sections:  yes
    fig_caption:      yes
    keep_tex:         yes
    latex_engine:     xelatex
    toc:              yes
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:    article
    classoption:      a4paper,oneside
    fontsize:         12pt
    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations:   yes
    colorlinks:       yes
    urlcolor:         blue
    biblio-style:     apalike
    bookdown::word_document2: default
---

### 2024-03-15 article/article.tex
Commit 2024-03-15 19:11

\caption{Daily mean values and trend of the CE over irradiance.}(\#fig:CEmeanDaily)
\end{figure}

@@

\caption{Treds of the mean over irradiance per CE}(\#fig:unnamed-chunk-1)
\end{figure}

@@

\caption{Trend of number of CE cases}(\#fig:unnamed-chunk-2)
\end{figure}

@@

\caption{Trend of the yearly excess energy due to CE over irradiance}(\#fig:unnamed-chunk-3)
\end{figure}

@@

\caption{Distribution of the number of CE cases}(\#fig:unnamed-chunk-4)
\end{figure}

@@

\caption{Distribution of CE above reference}(\#fig:unnamed-chunk-5)
\end{figure}

@@

\caption{Distribution of CE groups}(\#fig:unnamed-chunk-6)
\end{figure}

@@

\caption{Relation of mean over irradiance and CE group duration}(\#fig:unnamed-chunk-7)
\end{figure}

@@

\caption{Relation of maximun over irradiance and CE group duration}(\#fig:unnamed-chunk-8)
\end{figure}

@@

\caption{Distribution of the number of ECE cases}(\#fig:unnamed-chunk-9)
\end{figure}

@@

\caption{Distribution of ECE above 'clear sky' reference}(\#fig:unnamed-chunk-10)
\end{figure}

@@

\caption{Distribution of ECE Irradiance above 'TSI'}(\#fig:unnamed-chunk-11)
\end{figure}

@@

\caption{Distribution of }(\#fig:unnamed-chunk-12)
\end{figure}

@@

\caption{Distribution of }(\#fig:unnamed-chunk-13)
\end{figure}

>>>>

\caption{Daily mean values and trend of the CE over irradiance.}\label{fig:CEmeanDaily}
\end{figure}

@@

\caption{Treds of the mean over irradiance per CE}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\caption{Trend of number of CE cases}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\caption{Trend of the yearly excess energy due to CE over irradiance}\label{fig:unnamed-chunk-3}
\end{figure}

@@

\caption{Distribution of the number of CE cases}\label{fig:unnamed-chunk-4}
\end{figure}

@@

\caption{Distribution of CE above reference}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\caption{Distribution of CE groups}\label{fig:unnamed-chunk-6}
\end{figure}

@@

\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\caption{Relation of maximun over irradiance and CE group duration}\label{fig:unnamed-chunk-8}
\end{figure}

@@

\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-9}
\end{figure}

@@

\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-10}
\end{figure}

@@

\caption{Distribution of ECE Irradiance above 'TSI'}\label{fig:unnamed-chunk-11}
\end{figure}

@@

\caption{Distribution of }\label{fig:unnamed-chunk-12}
\end{figure}

@@

\caption{Distribution of }\label{fig:unnamed-chunk-13}
\end{figure}
